\documentclass[11pt,a4paper]{article}

% 页面边距设置（顶级投行标准的 0.5 英寸极限边距）
\usepackage[a4paper,margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage[hidelinks]{hyperref}

% 禁用缩进并设置字体
\setlength{\parindent}{0pt}
\raggedright

% 自定义章节标题格式 (全大写加粗，底部带横线)
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\vspace{-0.5em}\rule{\textwidth}{0.5pt}]
\titlespacing*{\section}{0pt}{10pt}{6pt}

% 自定义简历条目命令 (完全取消斜体，使用正体)
\newcommand{\resumeSubheading}[4]{
  \vspace{3pt}
  \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{#2} \\
    {#3} & {#4} \\
  \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[4]{
  \vspace{3pt}
  \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} $|$ {#2} & \textbf{#3} \\
    {#4} & \\
  \end{tabular*}\vspace{-4pt}
}

% 列表样式优化 (紧凑型)
\setlist[itemize]{leftmargin=0.15in, label={$\bullet$}, itemsep=1pt, parsep=0pt, topsep=2pt}

\begin{document}

% 头部联系方式
\begin{center}
    {\huge \textbf{MOCHIAO CHEN}} \\ \vspace{4pt}
    (+86) 186-1195-1800 $|$ \href{mailto:mochiaochen@gmail.com}{mochiaochen@gmail.com} \\ \vspace{2pt}
    \href{https://github.com/MochiaoChen}{github.com/MochiaoChen}
\end{center}

% 教育背景
\section{Education}
\resumeSubheading
  {University of International Business and Economics (UIBE)}{Beijing, China}
  {Bachelor of Economics in Banking and Finance}{Sept. 2024 -- Jun. 2028}

\section{Skills \& Awards}
\begin{itemize}[leftmargin=0in, label={}]
  \item \textbf{Technical Skills}: Python (Data Analysis), C++, SQL, HTML/JavaScript, LaTeX, Prompt Engineering, LLMs.
  \item \textbf{Analytical Skills}: Machine Learning, Statistical Modeling, Data Cleaning, Data Visualization.
  \item \textbf{Languages}: English (C1, CET-4: 626, Proficient in Academic Writing); Mandarin (Native).
  \item \textbf{Selected Awards}: 3rd Prize in 11th National College Student Statistical Modeling Competition (2025); 1st Prize in 37th Chinese Chemistry Olympiad (Shaanxi, 2023).
\end{itemize}
% 实习经历
\section{Professional Experience}
\resumeSubheading
  {CITIC Securities}{Beijing, China}
  {Investment Banking Intern}{Jan. 2026 -- Present}
\begin{itemize}
  \item Authored the Business chapter of a prospectus for an Embodied AI company's Hong Kong IPO by analyzing core business logic and conducting competitor research on AI algorithms and robot hardware chains.
  \item Assisted in completing Form M111 and drafting official replies to the Hong Kong Stock Exchange, ensuring rigorous compliance with HKEX listing standards and regulatory requirements.
\end{itemize}

\resumeSubheading
  {Great Wall Securities}{Beijing, China}
  {Investment Banking Intern}{Sept. 2025 -- Mar. 2026}
\begin{itemize}
  \item Conducted due diligence for corporate bond projects, drafted initiation reports, and managed working paper archiving.
  \item Utilized Wind, iFind, Excel, and Python for market data cleaning and financial peer analysis.
  \item Developed and deployed CLI agent scripts to automate document processing workflows, significantly enhancing operational efficiency.
\end{itemize}

\resumeSubheading
  {Yunshan Capital}{Beijing, China}
  {AI Tech Content Operations Intern}{Mar. 2025 -- Sept. 2025}
\begin{itemize}
  \item Published multiple industry analysis briefs focusing on AI and consumer sectors, deconstructing the business models and technological pathways of global AI startups.
  \item Established an AI investment topic library and generated in-depth analytical articles to support the investment team in evaluating macroeconomic trends and technology developments.
\end{itemize}

% 项目经历
\section{Selected Projects}
\resumeProjectHeading
  {"ICBC Cup" FinTech Innovation Competition}{Tech Lead}{Nov. 2025}{National 3rd Prize}
\begin{itemize}
  \item Engineered "Jianzhen Shield", a multimodal LLM-based anti-fraud portrait risk identification system targeting black market attacks in financial credit auditing.
  \item Designed a multi-agent architecture and utilized Prompt Engineering to identify 6 major fraud features, achieving 90\% accuracy on the test set and deploying a quantitative risk scoring mechanism.
\end{itemize}

\resumeProjectHeading
  {National Mathematical Modeling Competition}{Core Member}{Oct. 2025}{Beijing 1st Prize}
\begin{itemize}
  \item Built a multi-dimensional machine learning model based on clinical data to optimize Non-Invasive Prenatal Testing (NIPT) timing and anomaly detection.
  \item Handled missing value imputation and outlier removal; drafted the core abstract and utilized Python to plot data distributions, feature importance, and ROC curves.
\end{itemize}


% 附加信息与技能


\end{document}
